---
title: "Chapter 1 Demo"
author: "Kaitlyn Hoffmann"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---

# Create new Rmd

### Add a chunk
```{r}



```




#### Get the current working directory path (getwd()) and files (dir())
```{r}
getwd()

dir()

```

#### Set a path within a chunk for the working directory
```{r}
setwd("C:/Users/khoffmann/Desktop/BusinessAnalytics/Videos")
```


### Adding a new chunk to add a numerical variable called Price
```{r}
#Comments will be in green and ignored by R when running the chunk
#use a pound symbol (hashtag) to comment

#Display a value 20
20

#Assign the value 20 to a new variable called Price
Price = 20

#Display Price
Price

```

```{r}
#Change the value of Price from 20 to 30
Price = 30

#Display Price
Price

```

### Install a package called rmarkdown ;
- select line 43 and click on Run selected line or Ctrl+Enter (Cmd+Enter)
- having install.packages code within a chunk can cause issues when knitting to HTML

install.packages("rmarkdown") 


```{r}
#errors you may encounter

#case sensitivity
rm(Price)

#quotations
#student <- read.csv("student.csv") #this file is not in my working directory
#knitting issue if there is a code error

```





### Loading in data from the Excel (.csv) file ;
```{r}
#object name followed by the assignment statement then the funtion read.csv() with the filename saved to your computer in quotes within the parenthesis (object = read.csv("filename"))

realestate = read.csv("RealEstate_HouseData.csv")


```


### Display the object realestate ;
```{r}
#to display any object simply type the object name assigned

realestate

```










