---
title: "Chapter 3 Demo"
author: "Kaitlyn Hoffmann"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

## R Markdown

----------------------------------------------------------------------------------

## Create variables for the following and assign the value: 

-   name "[your name]"
-   year "Senior"
-   currentyear 2023


```{r}
name = "Kaitlyn"
year = "Senior"
currentyear = 2023


```

## Display the results and Check the class of each of the variables: name, year, currentyear, ID

-   results of each variable (what is the value)
-   class of each (what is the data type)

```{r}
#Results (display)
name
year
currentyear

#Class (data type)
class(name)
class(year)
class(currentyear)


```

## Change the data types as listed for the variables below:


-   name char (character)
-   year factor 
-   currentyear int (integer)


-   Rerun the class on each and display the results 

```{r}
#Change the data types 
year = as.factor(year)
currentyear = as.integer(currentyear)


#Display the data types using class
class(name)
class(year)
class(currentyear)


```

----------------------------------------------------------------------------------

# Nike Data for Cleaning and Manipulation

## Load/Create a data frame for the data file called nikedata.csv; call the object nike

```{r}

```

## Display the structure for nike
```{r}

```
## Display the first 10 rows for nike using head(); note: default is 6
```{r}

```

## Display the last 10 rows for nike using tail(); note: default is 6
```{r}

```

## Display the unique values for the following columns from the data frame nike:
-   note: this can also be used to create a new subset for only unique values (remove dups)

-   Events
-   Factory_Type
```{r}



```

## Display the column names for the data frame object called nike 
```{r}
#Can use either colnames(nike) or names(nike)



```

## Match the following column names and display the names after changing to confirm

-   Factory_Name 
-   Factory_Type
-   Product_Type
-   Brand 
-   Events
-   SupplierGroup
-   Address
-   City
-   State
-   Country_Region
-   Region
-   Total_Workers
-   Line_Workers
-   Perct_Female_Workers
-   Perct_Migrant_Workers

```{r}
#Change the column names




#Display column names




```

## Match the following data types and after run str() to check the changes: 

-   Factory_Name    |   chr
-   Factory_Type    |   factor   
-   Product_Type    |   factor
-   Brand           |   chr
-   Events          |   factor
-   SupplierGroup   |   chr
-   Address         |   chr
-   City            |   chr
-   State           |   chr
-   Country_Region  |   chr
-   Region          |   chr
-   Total_Workers   |   integer
-   Line_Workers    |   integer
-   Perct_Female_Workers  |   numeric     
-   Perct_Migrant_Workers |   numeric

```{r}
#Change the data types for data frame variables (columns)




#Display data frame structure (str)



```


## Display the number or rows and columns from nike (nrow and ncol)
```{r}
#number or rows



#number of columns


```

## Diplay the total number of NA values from the data frame nike using the following: 
-   is.na()
-   sum(is.na())
-   which(is.na())
```{r}
nike[nike==""] = NA #changes any "" to NA 




```

## Display the following rows: dataframe[rows, columns]
-   20
-   32
-   95

```{r}




```


## Display the following rows for columns 12 to 15:
-   20
-   32
-   95

```{r}


```

## Change a single value within nike for the following rows and columns:
-   Row 20, Column 1 = "ATOM"
-   Row 20, Column 12 = 120
-   Row 20, Column 13 = 68
-   Row 20, Column 14 = 62
-   Row 20, Column 15 = 38
-   Row 626, Column 14 = 64
```{r}




```


## Change multiple values within nike for Events:
-   use is.na to change all NA or Blanks within Events to "NONE"
-   use gsub to change all USA values to United States for Country_Region column

-   ^ start
-   $ stop
```{r}
#Change all NA values in Events to "NONE"
#sum(is.na(nike$Events)) #no NA values in Events? Because they loaded as ""
#nike$Events[nike$Events==""] = NA #changing the "" to NA
#nike$Events[is.na(nike$Events)] = "NONE" #now change using is.NA or use the below to do the same as the lines above with gsub (removes the step of converting "" to NA)
#nike$Events = gsub("^$", "NONE", nike$Events)

#Change NA to NONE for Events using is.na


#Change USA to United States for Country_Region using gsub





#Display unique values for Country_Region and Events

```

## Use na.omit to remove any rows with NA from nike creating a new data frame object called nike2
```{r}

```

## Calculate how many rows were removed using nrow
```{r}

```

## Add a new column to nike2 called Perct_Line_Workers based on Line_Workers divided by Total_Workers (use round(<calc>,2) to change the decimal places)
```{r}


```

## Create a new column to nike2 called NikeOnly based on whether the column Brand is equal to Nike 
```{r}


```

## Create a new column to nike2 called NotUSA based on whether the Country_Region is not equal to United States
```{r}


```

## Create a subset from nike2 based on whether the NotUSA column is equal to False and call it nikeUSA
```{r}


```

## Remove the column NotUSA from the data frame nikeUSA 
```{r}


```

## Create a subset from nike2 based on whether the nikeONLY column is equal to False using [Rows, Columns] call the new data frame nikeOTHER
```{r}


```

## Display an aggregate for nikeOTHER based on the Product_Type and average Total_Workers
```{r}


```
## Display an aggregate for nikeOTHER based on the Product_Type, Region and average Total_Workers
```{r}


```


## Display the sorted Country_Region column from nikeOTHER ascending 
```{r}


```

## Save the order/sort for the data in nikeOTHER ordered by the Country_Region column
```{r}


```



### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**