---
title: "Extra Credit 2"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

## R Markdown

----------------------------------------------------------------------------------

## Question 1: Load in the data house.csv as a data frame object called house
```{r}
house = read.csv("house.csv")
```

## Question 2: Display the first 5 rows of the data frame object house
```{r}
head(house,5)
```

## Question 3: Display the last 5 rows of the data frame object house
```{r}
tail(house,5)
```

## Question 4: Display the structure of the data frame house; look at the data types and make sure they are loaded appropriately
```{r}
str(house)
```

## Question 5: Display the total number of rows and columns in the data frame house
-   what does the number of rows represent (conceptually)? Look at the data, see what each row represents. Comment your response using # within the chunk.
```{r}
#number of rows (code)
nrow(house)
#number of columns (code)
ncol(house)

# what does the number of rows represent (conceptually)?
#Rows are equal to the number of houses
```

**ADD THE QUESTIONS BELOW AND A CHUNK FOLLOWING EACH TO THE EC2**
## Question 6: Basic calculations:
- What is the average lotsize from house?
- What is the average bedroom from house?
- What are the max tax from house?
- What is the spread/standard deviation (variation) tax from house?
- What is the range for tax from house?
```{r}
mean(house$lotsize)
mean(house$bedroom)
max(house$tax)
sd(house$tax)
max(house$tax)-min(house$tax)
```

## Question 7: Display the summary results for the data frame called house
```{r}
summary(house)

```

## Question 8: Display the summary results for each (BY) location separately for column 1 (value) only (points off if notcorrect view)
- Analyze the results
- Which location has the highest value on average (mean)? Comment your response using # within the chunk.
- Which location has the lowest value on average (mean)? Comment your response using # within the chunk.

```{r}
by(house[,1],house$location,summary)
#houseA
#houseE
```

## Question 9: Display a frequency table for style from the data frame house
- How many split level style houses? Comment your response using # within the chunk.
```{r}
table(house$style)
#46
```

## Question 10: Display a table summarizing the Average (mean) tax by style from the data frame house
```{r}
tapply(house$tax,house$style,mean)
```

## Question 11: Display/Plot the distribution for the value using the data frame house (histogram)
- add a color col="red"
- add a title main = "House Value Distribution Table"
```{r}
hist(house$value,main = "House Value Distribution Table",col = "red")
```

## Question 12: Display a boxplot for value from the data frame house
- add a color col = "limegreen"
- add a title main = "House Value Distribution"
```{r}
boxplot(house$value,main = "House Value Distribution",col = "limegreen")
```

## Question 13: Display a boxplot for value by location from the data frame house
- add a color col = "yellowgreen"
- add a title main = "House Value Distribution by Location"
```{r}
boxplot(house$value~house$location,main = "House Value Distribution by Location", col = "yellowgreen")
```

### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**