---
title: "Extra Credit 4"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

# Classification: Decision Trees
#-----------------------------------------------
Install the packages

install.packages("rpart")        #needs to be installed only once
install.packages("rpart.plot")  # needs to be installed only once

#-----------------------------------------------

## Load/Call each library (rpart and rpart.plot). Needs to be called each time
```{r}
library (rpart)
library (rpart.plot)
```




## Question 1: Read in the titanic data file and assign it to a data frame called titanic   
```{r}
titanic = read.csv("titanic.csv")
```

## Question 2: Remove the first two columns (Name and Ticket) before splitting the data into train and test/val
```{r}
titanic = titanic[,-c(1:2)]

```



## No Code needed, just run (Question 3): Now, we want to split the data frame titanic into 2 subsets (randomly). One to create/train the model and one to test/validate the model trained. The code in the chunk will do this for you and split the set into train using 70% of the rows; the remaining 30% of rows will be split into the test data frame. The code is also at the end of this document to explain what it is doing if you are interested. **Going forward, you will not use titanic (after you remove the first two columns and run the chunk to split the data frame titanic into two subsets--train and test).**

```{r}
## 70% of the sample size
smp_size <- floor(0.70 * nrow(titanic))
## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(titanic)), size = smp_size)
train <- titanic[train_ind, ]
test <- titanic[-train_ind, ]
```




**ADD REMAINING QUESTIONS FROM THE EC4.PDF**

## Question 4: Run the decision tree function (on the training data) to predict the Survived by using the other variables
```{r}
titanicModel = rpart(Survived~.,train,method="class")
```


## Question 5: Display the decision tree

```{r}
rpart.plot(titanicModel,type = 4,extra = 101)
```


## Question 6: Predict the Survived levels for the test data frame
```{r}
p = predict(titanicModel,test,type="class")
```


## Question 7: Add the predicted Survived types as a new column in the test/validation data call the new column titanicpredict
```{r}
test$predicted = p 
```


## Question 8: Display the contingency table between the observed and predicted Survived • Hint: observed variable/column: Survived | predicted variable/column: titanicpredict
```{r}
table(test$Survived,test$predicted)
```


## Question 9: Calculate the prediction accuracy of the decision tree model. Comment the accuracy % in the chunk. 

```{r}
table(test[ ,c(1,9)])
(139+69)/nrow(test)
#77.6% accurate
```


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**



