---
title: "Extra Credit 5"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

#   Optimization: Extra Credit

## Questions:

### Question 1: Formulate the linear programming model for this problem.
-   Use # to comment below each question (for each line)
```{r}
#----------------------------------
#a. Define the decision variables
#Super coffee = s
#Deluxe coffee = d

 
#----------------------------------
#b. Formulate the objective function
     
#maximize profit = 0.22s+0.3D

    
 
#----------------------------------
#c. State the constraints.
# **LABEL THE CONSTRAINT | Do not forget to also list the non-negativity constraints**


#brazil 0.5s + 0.25d <= 120 brazilian blend kg
#Columbian 0.5s + 0.75d <= 160 columbian kg 

#s,d>=0


#----------------------------------
``` 
 

### Install lpSolve and run the library

-   select the line below and click on Run selected line or Ctrl+Enter (Cmd+Enter)
-   having install.packages code within a chunk can cause issues when knitting to HTML


install.packages("lpSolve")



### Load the lpSolve library to use the lp function
-   Call the library function "lpSolve". You need to execute this library function each time when you run linear programming
```{r}
#no code needed this chunk, just run it
library (lpSolve) 
```




### Question 2:	Enter the problem data and find the optimum solution for this problem using R Studio 
-   Load the elements: 

-   objective, constr, constr.dir, rhs (from cheat sheet)  -OR-
-   ObjFunc, LeftSide, OpDirections, RightSide (from textbook/demo) 

```{r}

ObjFunc = c(0.22, 0.3) #-   #maximize profit = 0.22s+0.3D

leftsidevector = c(0.5,0.25,0.5,0.75)

LeftSide = matrix(leftsidevector, nrow = 2, byrow=TRUE)

OpDirections = c("<=","<=")
RightSide = c(120,160)

```

### Question 3: Run the lp function (optimum code from cheat sheet; lpmodel from textbook/demo)
```{r}
lpmodel = lp(direction = "max", ObjFunc, LeftSide, OpDirections, RightSide, compute.sens = T)
```


### Question 4: Display the solutions from the optimum solution 
-   a. Display the solution values 
-   b. Display the objective value 
-   c. Display the dual values 
```{r}
lpmodel$solution
lpmodel$objval
lpmodel$duals

```

### Question 5: Answer the questions inside the chunk using # to comment 
-   a. What are the dual values? List and label each.
-   b. How much would the profit increase if we had 10 more kg of Colombian coffee on hand?
```{r}
# a. What are the dual values? List and label each.

#0.06 brazilian
#0.38 columbian 
#0.00 super 
#0.00 deluxe

# b. How much would the profit increase if we had 10 more kg of Colombian coffee on hand?


#3.8 dollars


```




### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

