---
title: "Business Analytics Homework1Part2"
author: "Ryan Hensley"
output:
  html_document: 
    code_download: TRUE
    toc: TRUE
---

**Set the sub folder (where you have saved the files) as the working directory: Click Session --\> Set Working Directory --\> Choose Directory ... and select he sub folder where you saved the downloaded file(s) and click on OK.**



### Formatting in R Markdowns

### Creates a header (need the space between the # and first character/text)
-   creates a bullet point (dash followed by a tab)

**bolds the text**



## Question 1: (Starting with the first chunk) Complete the following basic operations:
-	Create/load an object called School and assign the value “Loyola” to School.
-	Create/load an object called Freshman and assign the value 2985 (do not use a comma in 2985)
-	Create/load an object called Soph and assign the value 3101 (do not use a comma in 3101)
-	Create/load an object called Jr and assign the value 2848 (do not use a comma in 2848)
-	Create/load an object called Senior and assign the value 3250 (do not use a comma in 3250)
```{r}
School = "Loyola"
Freshman = 2985
Soph = 3101
Jr = 2848
Senior = 3250


```

## Question 2:  Displaying the values of variable objects (remember, just type the object name and run the chunk)
-	Display the value assigned to the object School 
-	Display the value assigned to the object Freshman 
-	Display the value assigned to the object Soph 
-	Display the value assigned to the object Jr 
-	Display the value assigned to the object Senior
```{r}
School
Freshman
Soph
Jr
Senior

```


## Question 3:  Basic calculations with objects (remember, just use R as a calculator: + , -, *, /)
-	Display the value of Freshman + Soph + Jr + Senior (use the object names within the math problem, the values will be passed to get the result)
-	Create/load an object called Enrolled and assign the value of Freshman + Soph + Jr + Senior (use the object names within the math problem, the values will be passed to get the result)
```{r}
Freshman + Soph + Jr + Senior
Enrolled = Freshman + Soph + Jr + Senior
Enrolled
```

## Question 4: Create a vector for the following (vectors use c() to combine different values into a one-dimensional object)
-	Note: Vectors are loaded using the c() function. Separate each value with a comma. Remember, do not put quotes “” around numbers. For any text values, surround each value with quotes. Example: Name = c(“Kaitlyn”, “Hoffmann”)
-	Create/load an object called Grades with the values 86, 92, 99
-	Create/load an object called Ages with the values 19, 26, 20
-	Create/load an object called Class with the values Jr, Sr, Sr
```{r}
Grades = c(86,92,99)
Ages = c(19,26,20)
Class = c("Jr","Sr","Sr")
#This question had seniors doubled on the pdf. I do not know if this was intentional or not but I have followed the procedure as it was listed 

```

## Question 5: Displaying the values of vector objects
-	Display the values assigned to the object Grades
-	Display the values assigned to the object Ages
-	Display the values assigned to the object Class
```{r}
Grades
Ages
Class


```



**ADD THE QUESTIONS BELOW AND A CHUNK FOLLOWING EACH TO THE HW1P2.RMD**

## Question 6: Calculate the following using the vector objects and summary calculations (mean, median, sd, etc.)
- Display the average (mean) of Grades -- example: mean(Grades)
- Display the average (mean) of Ages
- Display the standard deviation (sd) of Grades

```{r}
mean(Grades)
mean(Ages)
sd(Grades)
```

## Question 7: Creating/Loading in data frame objects from data files
**This will import the data in the files to the data frame object student and customer**
- Note: Save the file student.csv from SAKAI to the working directory folder location you have set
- Note: Save the file customer.txt from SAKAI to the working directory folder location you have set; going forward
we will always use .csv but this leads as an example of how a .txt file can be used to load data as well
- Create/load the data “student.csv” using read.csv and call the object Student
student = read.csv(“student.csv”)
- Create/load the data “customer.txt” using read.delim and call the object Customer
customer = read.delim(“customer.txt”, header = TRUE)
```{r}
student = read.csv("student.csv")
customer = read.delim("customer.txt", header = TRUE)

```


## Question 6: Calculate the following using the data frame objects and summary calculations (mean, median, sd, etc.)
- Display the average (mean) of the column weight from the object student -- example: mean(student$weight)
- Display the average (mean) of the column height from the object customer
```{r}
mean(student$weight)
mean(customer$height)
```

## Question 7: Display the summary results for a data frame object
- Display the summary results for the object student -- example: summary(student)
```{r}
summary(student)
```

## Question 8: Display the summary results for a data frame object
- Display the summary results for the object customer
```{r}
summary(customer)
```

## CREATE HTML FILE (no chunk needed for this)
- Create an html file that will contain:
- All the code
- Executed outputs and answers to the follow-up questions, if there is any.
- Click the arrow next to Knit and choose HTML
- This process will save the Rmd file and create the html file on your working directory.

