---
title: "Business Analytics Homework2"
author: "Ryan Hensley"
output:
  html_document: 
    code_download: TRUE
    toc: TRUE
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**



### Formatting in R Markdowns

### Creates a header (need the space between the # and first character/text)
-   creates a bullet point (dash followed by a tab)

**bolds the text**


# Start Below

## Question 1: Create a variable object (left) and assign the value to each (right)
-   Course        "INFS 343"
-   Semester      "Fall"
-   Year          2023
-   Location      "SCHR302"
-   School        "Loyola"

```{r}
Course = "INFS 343"
Semester = "Fall"
Year = 2023
Location = "SCHR302"
School = "Loyola"
```

## Question 2:  Displaying the values of variable objects 
-   Course 
-   Semester 
-   Year
-   Location 
-   School 
```{r}
Course
Semester
Year
Location
School

```


## Question 3:  Displaying the class of each variable object -   Course 
-   Semester 
-   Year
-   Location 
-   School 
```{r}
class(Course)
class(Semester)
class(Year)
class(Location)
class(School)

```


## Question 4:  Remove the objects using rm()
- 	Course 
- 	Semester 
- 	Year
- 	Location 
- 	School 
```{r}

rm(Course)
rm(Semester)
rm(Year)
rm(Location)
rm(School)



```


## Question 5:  Create a vector object for each of the variables/columns below and assign the elements/values. Use quotes for the character values; do not use quotes for numeric/integer values. The object names are Division, City, Team, Wins, Loss, Tie.

- 	Division    	City        	Team     	Wins    Loss   Tie
- 	AFC North   	Cleveland   	Browns   	1      	 0       0
- 	AFC North  	  Baltimore   	Ravens   	1      	 0       0
- 	AFC North  	  Pittsburgh  	Steelers 	0     	 1       0
- 	AFC North   	Cincinnati  	Bengals  	0     	 1       0
- 	NFC North   	Green Bay   	Packers  	1    	   0       0
- 	NFC North   	Detroit     	Lions    	1     	 0       0
- 	NFC North   	Minnesota   	Vikings 	0     	 1       0
- 	NFC North   	Chicago    	  Bears    	0     	 1       0
```{r}
Division = c("AFC North","AFC North","AFC North", "AFC North", "NFC North", "NFC North","NFC North","NFC North")
City = c("Cleveland","Baltimore","Pittsburgh","Cincinnati","Green Bay", "Detroit","Minnesota","Chicago")
Team = c("Browns","Ravens","Steelers","Bengals","Packers","Lions","Vikings","Bears")
Wins = c(1,1,0,0,1,1,0,0)
Loss = c(0,0,1,1,0,0,1,1)
Tie = c(0,0,0,0,0,0,0,0)



```

**ADD THE QUESTIONS BELOW AND A CHUNK FOLLOWING EACH TO THE HW2.RMD**
## Question 6: Display the values/elements of each vector object.
Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.
- Division
- City
- Team
- Wins
- Loss
- Tie
```{r}
Division
City
Team
Wins
Loss
Tie
```

## Question 7: Display the class of each vector object. Wins, Loss, and Tie should NOT be character (chr) or factor.
- Division
- City
- Team
- Wins
- Loss
- Tie
```{r}
class(Division)
class(City)
class(Team)
class(Wins)
class(Loss)
class(Tie)
```

## Question 8: Create a logical vector (Local) that will check the Division vector--if the division is == "AFC North". Call this new logical vector Local. **Review the slides and text for creating logical vectors.**
```{r}
Local = Division == "AFC North"
Local
```

## Question 9: Display the length of each vector object.
- Division
- City
- Team
- Wins
- Loss
- Tie
- Local
```{r}
length(Division)
length(City)
length(Team)
length(Wins)
length(Loss)
length(Tie)
```

## Question 10: Create a new data frame object called NFLnorth and combine the vectors below:
- Division
- City
- Team
- Wins
- Loss
- Tie
- Local
```{r}
NFLnorth = data.frame(Division,City,Team,Wins,Loss,Tie,Local)
```

## Question 10: Display the new data frame object called NFLnorth.
```{r}
NFLnorth
```

## Question 11: Display the structure str() for the data frame object NFLnorth
```{r}
str(NFLnorth)
```

## Question 12: Run the summary() function to gather the summary statistics for the data frame NFLnorth
```{r}
summary(NFLnorth)
```

## Question 13: Run the code table(NFLnorth$Division) to see the count/frequency of teams for each division
```{r}
table(NFLnorth$Division)
```

## Question 14: Create the following Matrix and call the matrix object mat1:
- 1 3 5
- 20 24 40
- 54 1 20
```{r}
mat1=matrix(c(1,3,5,20,24,40,54,1,20),ncol = 3,byrow = TRUE)
```

## Question 15: Display mat1
```{r}
mat1
```

### CREATE HTML FILE

```

```











