---
title: "Business Analytics Homework3"
author: "Ryan Hensley"
output:
  html_document: 
    code_download: TRUE
    toc: TRUE
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

## R Markdown

### Formatting in R Markdowns

### Creates a header (need the space between the # and first character/text)
-   creates a bullet point (dash followed by a tab)

**bolds the text**


# Start Below

## Question 1: Load/Create a data frame for the data file called jobdesc.csv; call the object jobs
-   taken as a sample/subset from https://www.kaggle.com/datasets/ravindrasinghrana/job-description-dataset

```{r}
jobs = read.csv("jobdesc.csv")

```

## Question 2: Display the structure for the data frame jobs
```{r}
str(jobs)
```

## Question 3: Display the first 10 rows for jobs using head(); note: default is 6
```{r}
head(jobs,10)
```

## Question 4: Display the last 10 rows for jobs using tail(); note: default is 6
```{r}
tail(jobs,10)
```

## Question 5: Display the unique values for the following columns from the data frame jobs:

-   location
-   Work.Type
-   Preference
```{r}
unique(jobs$location)
unique(jobs$Work.Type)
unique(jobs$Preference)

```

## Question 6: Display the column names for the data frame object called jobs 
```{r}

colnames(jobs)

```

## Question 7: Match the following column names and display the names after changing to confirm

-   Job_ID 
-   Experience
-   Qualifications
-   Salary_Range 
-   Location
-   Country
-   latitude
-   longitude
-   Work_Type
-   Company_Size
-   Job_Post_Date
-   Preference
-   Contact_Person
-   Contact
-   Job_Title
-   Role 
-   Job_Portal
-   Company

```{r}
#Change the column names
colnames(jobs)[1] = "Job_ID" 
colnames(jobs)[4] = "Salary.Range" 
colnames(jobs)[5] = "Location"
colnames(jobs)[9] = "Work_Type" 
colnames(jobs)[10] = "Company_Size" 
colnames(jobs)[11] = "Job_Post_Date"
colnames(jobs)[13] = "Contact_Person" 
colnames(jobs)[15] = "Job_Title"
colnames(jobs)[17] = "Job_Portal" 



#Display column names
colnames(jobs)


```

## Question 8: Match the following data types and after run str() to check the changes: 


-   Job_ID as a character
-   Experience as a character
-   Qualifications as a factor
-   Salary_Range as a character
-   Location as a factor
-   Country as a factor
-   latitude as numeric
-   longitude as numeric
-   Work_Type as a factor
-   Company_Size as an integer
-   Job_Post_Date as a character
-   Preference as a factor
-   Contact_Person as a character
-   Contact as a character
-   Job_Title as a character
-   Role as a character
-   Job_Portal as a character
-   Company as a character

```{r}
#Change the data types for data frame variables (columns)
jobs$Job_ID = as.character(jobs$Job_ID)
jobs$Experience = as.character(jobs$Experience)
jobs$Qualifications = as.factor(jobs$Qualifications)
jobs$Salary.Range = as.character(jobs$Salary.Range)
jobs$Location = as.factor(jobs$Location)
jobs$Country = as.factor(jobs$Country)
jobs$latitude = as.numeric(jobs$latitude)
jobs$longitude = as.numeric(jobs$longitude)
jobs$Work_Type = as.factor(jobs$Work_Type)
jobs$Company_Size = as.integer(jobs$Company_Size)
jobs$Job_Post_Date = as.character(jobs$Job_Post_Date)
jobs$Preference = as.factor(jobs$Preference)
jobs$Contact_Person = as.character(jobs$Contact_Person)
jobs$Contact = as.character(jobs$Contact)
jobs$Job_Title = as.character(jobs$Job_Title)
jobs$Role = as.character(jobs$Role)
jobs$Job_Portal = as.character(jobs$Job_Portal)
jobs$Company = as.character(jobs$Company)


#Display data frame structure (str)

str(jobs)

```



**ADD THE QUESTIONS BELOW AND A CHUNK FOLLOWING EACH TO THE HW3.RMD**

## Question 10: Diplay the total number of NA values from the data frame jobs using the following:
- is.na()
- sum(is.na())
- which(is.na())
```{r}
is.na(jobs)
sum(is.na(jobs))
which(is.na(jobs))
```

## Question 11: Display the following rows: dataframe[rows, columns] for all columns
- 5
- 6
- 9
```{r}
jobs[c(5,6,9),] 
```

## Question 12: Display the following rows for columns 3 and 10 (not 3 to 10):
- 3
- 10
```{r}
jobs[c(3,10),]
```

## Question 13: Change a single value within jobs for the following rows and columns:
- Change the Qualifications for Row 5 to MCA
- Change the Qualifications for Row 6 to MCA
- Change the Company Size for Row 9 to 68152
- Change the Preference for Row 1 to Both
```{r}
jobs[5,3] = "MCA"
jobs[6,3] = "MCA"
jobs[9,10] = 68152
jobs[1,12] = "Both"
```


## Question 14: Change multiple values within jobs for Work_Type:
- use gsub to change all values set to "Temporary" to "Temp" for the column Work_Type
```{r}
 jobs$Work_Type = gsub("Temporary", "Temp", jobs$Work_Type)
```

## Question 15: Remove the columns latitude, longitude, and Contact from the data frame jobs
```{r}
jobs$latitude = NULL
jobs$longitude = NULL
jobs$contact = NULL

```

## Question 16: Use na.omit to remove any rows with NA from jobs creating a new data frame object called jobs2
```{r}
jobs2  = na.omit(jobs)
```

------------------------- NOW USING JOBS 2 ---------------------------------------
## Question 17: Create a new column to jobs2 called NoPref based on whether the column Preference is equal to Both
(meaning, if the value is Both then True so no preference)
```{r}
jobs2$NoPref = jobs2$Preference == "Both"
```

## Question 18: Create a subset from jobs2 based on whether the NoPref column is not equal to True and call it FlaggedJobs
```{r}
# Create the subset
FlaggedJobs =  subset(jobs2,jobs2$NoPref == FALSE)

```

## Question 19: Display an aggregate for jobs2 based on the Role and average Company_Size
```{r}
aggregate(Company_Size~Role, data = jobs2, mean)
```

## Question 20: Save the order/sort for the data in jobs2 ordered by the Company column
```{r}
jobs2 = jobs2[order(jobs2$Company, decreasing = FALSE), ]
```






### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**