---
title: "Homework 4"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

## R Markdown

----------------------------------------------------------------------------------

## Question 1: Load in the data starbucksmenu.csv as a data frame object called sbux
```{r}
sbux = read.csv("starbucksmenu.csv")
```

## Question 2: Display the first 8 rows of the data frame object sbux
```{r}
head(sbux,8)
```

## Question 3: Display the first 10 rows of the data frame object sbux
```{r}
head(sbux,10)

```

## Question 4: Display the last 6 rows of the data frame object sbux
```{r}
tail(sbux)
```


## Question 5: Display the structure of the data frame sbux; look at the data types and make sure they are loaded appropriately
-   display the structure (should only be 3 chr characters)
-   Bucket the categorical vs numerical variables/columns. Comment your response using # within the chunk.
```{r}
#str (code)
str(sbux)

#categorical: Beverage_category,beverage, beverage_prep
#numerical: Calories,Total_Fat_g,Trans_Fat_g,Saturated_Fat_g,Sodium_mg,Total_Carbs_g,Cholesterol_mg,Fiber_g,Sugar_g, Protein_g,VitaminA_PercDV,VitaminC_PercDV,Calcium_PercDV,Iron_PercDV,Caffeine_mg
```

## Question 6: Display the total number of rows and columns in the data frame sbux
-   what does the number of rows represent (conceptually)? Look at the data, see what each row represents. Comment your response using # within the chunk.
```{r}
#number of rows (code)
nrow(sbux)
#number of columns (code)
ncol(sbux)

# what does the number of rows represent (conceptually)?:The number of rows represents the number of orders

```

**ADD THE QUESTIONS BELOW AND A CHUNK FOLLOWING EACH TO THE HW4.RMD**

## Question 7: Basic calculations:
- What is the average Calories from sbux?
- What is the average Caffeine_mg from sbux?
- What are the max Calories from sbux?
- What is the spread/standard deviation (variation) Calories from sbux?
- What is the range for Calories from sbux?
```{r}
mean(sbux$Calories)
mean(sbux$Caffeine_mg)
max(sbux$Calories)
sd(sbux$Calories)
max(sbux$Calories) - min(sbux$Calories)
```

## Question 8: Display the summary results for the data frame called sbux
- What is the average calories for the drinks? Comment your response using # within the chunk.
```{r}
summary(sbux)
#avg is 198
```

## Question 9: Display the summary results for each (BY) Beverage_category separately for column 4 (Calories) only
(points off if not correct view)
- Analyze the results
- Which beverage category has the highest calories on average (mean)? Comment your response using # within the
chunk.
- Which beverage category has the lowest calories on average (mean)? Comment your response using # within the
chunk.
- Which beverage category has the highest calories (max)? Comment your response using # within the chunk.
```{r}
by(sbux[,4],sbux$Beverage_category,summary)
#highest average calories is Frappuccino
#Lowest average calories is Coffee
#Single Max highest calories is Espresso
```

## Question 10: Display a frequency table for Beverage_category from the data frame sbux
- How many Classic Espresso Drinks are available on the menu? Comment your response using # within the chunk.
```{r}
table(sbux$Beverage_category)
#98
```

## Question 11: Display a table summarizing the Average (mean) Caffeine_mg by Beverage_category from the data frame
sbux
- Which category has the highest overall average mg of caffeine? Comment your response using # within the chunk.
- Which category has the lowest overall average mg of caffeine? Comment your response using # within the chunk.
```{r}
tapply(sbux$Caffeine_mg,sbux$Beverage_category,mean)
#Highest AVG Caffeine is Coffee
#Lowest AVG Caffeine is Tea
```

## Question 12:
- Display the summarized standard deviation (sd) Caffeine_mg by Beverage_category for sbux
- Display the summarized average (mean) Calories by Beverage_category for sbux
```{r}
tapply(sbux$Caffeine_mg,sbux$Beverage_category,sd)
tapply(sbux$Calories,sbux$Beverage_category,mean)
```

## Question 13: Display/Plot the distribution for the Calories using the data frame sbux (histogram)
- add a color col="darkseagreen4"
- add a title main = "Calorie Distribution Table for Starbucks Drinks"
```{r}
hist(sbux$Calories,main = "Calorie Distribution Table for Starbucks Drinks", col="darkseagreen4")
```


## Question 14: Display a boxplot for Calories from the data frame sbux
- add a color col = "limegreen"
- add a title main = "Calorie Distribution for Starbucks Drinks"
- Based on the output, how many outliers are in the data? Comment your response using # within the chunk.
- Approximately, what is the first quartile? What is the second quartile? Comment your response using # within the
chunk.
```{r}
boxplot(sbux$Calories,main = "Calorie Distribution for Starbucks Drinks",col = "limegreen")
#1 outlier 
# First quartile is 125, second quartile is 200
```

## Question 15: Display a boxplot for Calories by Beverage_category from the data frame sbux
- add a color col = "yellowgreen"
- add a title main = "Calorie Distribution by Beverage Category for Starbucks Drinks"
```{r}
boxplot(sbux$Calories~sbux$Beverage_category,main = "Calorie Distribution by Beverage Category for Starbucks Drinks",col = "yellowgreen")
```

## Question 16: Display a boxplot for Caffeine_mg by Beverage_category from the data frame sbux
- add a color col = "lightgreen"
- add a title main = "Caffeine(mg) Distribution by Beverage Category for Starbucks Drinks"
- Does Coffee or Espresso have higher caffeine? Comment your response using # within the chunk.
```{r}
boxplot(sbux$Caffeine_mg~sbux$Beverage_category,main = "Caffeine(mg) Distribution by Beverage Category for Starbucks Drinks",col = "lightgreen")
#Coffee
```

## Question 17: Display a scatterplot for Calories (x) and Sugar_g (y) from sbux [Hint: plot(x, y)]
- add a color col = "blue"
- add a title main = "Starbucks: Calories and Sugar"
- Does Calories and Sugar have a positive relationship/trend? Comment your response using # within the chunk. Yes or
No

```{r}
plot(sbux$Calories,sbux$Sugar_g, main = "Starbucks: Calories and Sugar",col = "blue")
#Positive
```

## Question 18: Use par(mfrow=c(2,2)) to display the following plots in 2 row 2 columns on the output
- Display a scatterplot for Calories (x) and Sugar_g (y) from sbux (col = "blue")
- Display a scatterplot for Calories (x) and Total_Carbs_g (y) from sbux (col = "palegreen3")
- Display a histogram distribution for Calories from sbux (col = "seagreen4")
- Display a boxplot for Caffeine_mg by Beverage_category from the data frame sbux (col = "limegreen")

```{r}
par(mfrow=c(2,2))
plot(sbux$Calories,sbux$Sugar_g,col = "blue")
plot(sbux$Calories,sbux$Total_Carbs_g,col="palegreen3")
hist(sbux$Calories,col="seagreen4")
boxplot(sbux$Caffeine_mg~sbux$Beverage_category,col = "limegreen")
```



### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**