---
title: "Homework 5"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

# Data, Plots, Correlation Coefficient
Data taken from: https://www.kaggle.com/datasets/kumarajarshi/life-expectancy-who/data


## Read the data from LifeExpectancyData.csv creating a new data frame called life 
```{r}
life = read.csv("LifeExpectancyData.csv")
```

## Display the top 10 rows of the data in life data frame
```{r}
head(life,10)
```

## Display the column names in life data frame
```{r}
colnames(life)
```


## Plot the following: par(mfrow=c(1,2))
-   a.	Plot of LifeExpectancy vs AdultMortality	(LifeExpectancy should be on Y axis) (x,y) | col = "grey" | main="Life Expectancy and Adult Mortality"
-   abline(lm(LifeExpectancy~AdultMortality, data=life),lwd = 2, col="red")
-   b.	Plot of LifeExpectancy vs BMI	(LifeExpectancy should be on Y axis) (x,y) | col = "grey" | main="Life Expectancy and BMI"
-   abline(lm(LifeExpectancy~BMI, data=life),lwd = 2, col="darkgreen")
```{r}
par(mfrow=c(1,2))
plot(life$AdultMortality,life$LifeExpectancy,main="Life Expectancy and Adult Mortality",col="grey")
abline(lm(LifeExpectancy~AdultMortality, data=life),lwd = 2, col="red")
plot(life$BMI,life$LifeExpectancy,main="Life Expectancy and BMI",col="grey")
abline(lm(LifeExpectancy~BMI, data=life),lwd = 2, col="darkgreen")

```

## Display the following 9 plots in 3 rows and 3 columns (the code all must go in the same chunk—each on a new line): par (mfrow=c(3,3))
 
-    a.	LifeExpectancy vs AdultMortality  main="Life Expectancy and Adult Mortality"
-    b.	LifeExpectancy vs InfantDeaths    main="Life Expectancy and InfantDeaths"
-    c.	LifeExpectancy vs Alcohol        main="Life Expectancy and Alcohol"
-    d.	LifeExpectancy vs Perct_Expenditure  main="Life Expectancy and Perct_Expenditure"
-    e.	LifeExpectancy vs HepatitisB main="Life Expectancy and HepatitisB"
-    f.	LifeExpectancy vs Measles  main="Life Expectancy and Measles"
-    g. LifeExpectancy vs BMI main="Life Expectancy and BMI"
-    h. LifeExpectancy vs Polio  main="Life Expectancy and Polio"
-    i. LifeExpectancy vs TotalExpenditure  main="Life Expectancy and TotalExpenditure"

-   Add a linear regression line to each plot for bullet points a through i above. abline(lm(dependent~independent, data=life), lwd=2, col="red")

-   Determine whether each independent variable has a positive or negative relationship with LifeExpectancy. Answer Negative and Positive within the chunk (comment)
```{r}
par (mfrow=c(3,3))
  plot(life$AdultMortality,life$LifeExpectancy,main="Life Expectancy and Adult Mortality")
  abline(lm(LifeExpectancy~AdultMortality, data=life), lwd=2, col="red")

  plot(life$InfantDeaths,life$LifeExpectancy,main="Life Expectancy and InfantDeaths")
  abline(lm(LifeExpectancy~InfantDeaths, data=life), lwd=2, col="red")

  plot(life$Alcohol,life$LifeExpectancy,main="Life Expectancy and Alcohol")
  abline(lm(LifeExpectancy~Alcohol, data=life), lwd=2, col="red")

  plot(life$Perct_Expenditure,life$LifeExpectancy,main="Life Expectancy and Perct_Expenditure")
  abline(lm(LifeExpectancy~Perct_Expenditure, data=life), lwd=2, col="red")

  plot(life$HepatitisB,life$LifeExpectancy,main="Life Expectancy and HepatitisB")
  abline(lm(LifeExpectancy~HepatitisB, data=life), lwd=2, col="red")

  plot(life$Measles,life$LifeExpectancy,main="Life Expectancy and Measles")
  abline(lm(LifeExpectancy~Measles, data=life), lwd=2, col="red")

  plot(life$BMI,life$LifeExpectancy,main="Life Expectancy and BMI")
  abline(lm(LifeExpectancy~BMI, data=life), lwd=2, col="red")

  plot(life$Polio,life$LifeExpectancy,main="Life Expectancy and Polio")
  abline(lm(LifeExpectancy~Polio, data=life), lwd=2, col="red")

  plot(life$TotalExpenditure,life$LifeExpectancy,main="Life Expectancy and TotalExpenditure")
  abline(lm(LifeExpectancy~TotalExpenditure, data=life), lwd=2, col="red")

#Positive Relationship: Alcohol, Perct_Expenditure,HepetitisB,BMI,Polio,TotalExpenditure
#Negative Relationship:AdultMortality,InfantDeaths,Measles 
```


## Calculate the following correlation coefficients: **columns 4 through 19**

-    a.	LifeExpectancy and AdultMortality 
-    b.	LifeExpectancy and InfantDeaths 
-    c.	LifeExpectancy and Alcohol
-    d.	LifeExpectancy and Perct_Expenditure 
-    e.	LifeExpectancy and HepatitisB 
-    f.	LifeExpectancy and Measles
-    g.	LifeExpectancy and BMI
-    h.	LifeExpectancy and Polio
-    i.	LifeExpectancy and TotalExpenditure
-    j.	LifeExpectancy and Diphtheria
-    k.	LifeExpectancy and HIV_AIDS
-    l.	LifeExpectancy and GDP
-    m.	LifeExpectancy and Population
-    n.	LifeExpectancy and IncomeComp
-    o.	LifeExpectancy and Schooling

### Which variable has the highest correlation with LifeExpectancy? Which variable has the second highest correlation with LifeExpectancy?
```{r}
cor(life$LifeExpectancy,life[,4:19])


#Highest Correlation Coefficient: IncomeComp
#Second: Schooling
```

# Regression: Simple Linear Regression Problem 1 

## Complete the following: Regression Model and Summary

-   Use a simple regression model to predict the LifeExpectancy by using AdultMortality. Call this model as LR1
**"Adult Mortality Rates of both sexes (probability of dying between 15 and 60 years per 1000 population)"**
-   Display the summary calculations for LR1
```{r}
options(scipen=999)
#------------------------------------------
#Regression Model:
LR1 = lm(LifeExpectancy~AdultMortality,data=life)


#------------------------------------------
#Summary of Model:

summary(LR1)

#------------------------------------------
```


## Complete the following:  **Answer in chunk as a comment**: 

-   What is the estimated regression equation?
-   What percentage of the total variation in LifeExpectancy is explained by the regression (R2)?
-   Is AdultMortality significant in predicting the LifeExpectancy at significance level of 0.05? To answer this question, we need to test Ho that H1= 0 against the two-sided alternative. Should the null hypothesis be accepted or rejected at a 0.05 significance level?

```{r}
#------------------------------------------
#Regression Equation:  
#Answer:  y = 78.018216-0.053358x 


#------------------------------------------
#R2:
##Answer: 48.49% of the variation is is explained by the independent variable in the model



#------------------------------------------
#Hypothesis Testing:AdultMortality

#Answer p-value: <0.0000000000000002 pvalue < 0.05
#Decision/Response: Reject the null hypothesis [that AdultMortality is not significant]; AdultMortality is significant in predicting LifeExpectancy


#------------------------------------------
```


## Complete the following: Prediction and Confidence Interval

-   Calculate the predicted average LifeExpectancy for a country with an AdultMortality rate of 280.
-   Construct a 95 percent confidence interval estimate for the mean LifeExpectancy of the country with an AdultMortality rate of 280. (include correct interpretation)
```{r}
#------------------------------------------
#Predict Code
78.018216-(0.053358*280)

#Answer/Statement: the predicted average LifeExpectancy for a country with an AdultMortality rate of 280 Is 63.07798 years
#------------------------------------------
#Confidence Interval Code
predict(LR1, data.frame(AdultMortality=280), interval="confidence")


#------------------------------------------
#Confidence Interval Interpretation Response/Statement: With 95% confidence, we can say the life expectancy with an adult mortality rate of 280 would have a life expectancy between 62.74005 and 63.41564
#------------------------------------------
```


# Regression: Multiple Regression Problem 1


## Complete the following: Regression Model and Summary

-   Use a multiple regression model to predict the LifeExpectancy (Y) by using AdultMortality (X1), Schooling (X2), and IncomeComp (X3). Call this model as LR3. 
**LifeExpectancy: Life Expectancy in age** | 
**AdultMortality: Adult Mortality Rates of both sexes (probability of dying between 15 and 60 years per 1000 population)** | 
**Schooling: Number of years of Schooling(years)** | 
**IncomeComp: Human Development Index in terms of income composition of resources (index ranging from 0 to 1)**

-   Display the summary calculations for LR3.

```{r}
options(scipen=999)
#------------------------------------------
#Regression Model:
LR3= lm(LifeExpectancy~AdultMortality+Schooling+IncomeComp, data=life)


#------------------------------------------
#Summary of Model:
summary(LR3)



#------------------------------------------
```

## Complete the following:  **Answer in chunk as a comment**: 

-   What is the estimated regression equation?
-   What percentage of the total variation in LifeExpectancy is explained by the regression (R2)?
-   Is Schooling significant in predicting the LifeExpectancy at significance level of 0.05? To answer this question, we need to test Ho that H1= 0 against the two-sided alternative. Should the null hypothesis be accepted or rejected at a 0.05 significance level?
-   Is IncomeComp significant in predicting the LifeExpectancy as at significance level of 0.05? To answer this question, we need to test Ho that H1= 0 against the two-sided alternative. Should the null hypothesis be accepted or rejected at a 0.05 significance level?
```{r}
#------------------------------------------
#Regression Equation:
#Answer: y= 66.1092771 - 0.0411909adultmortality + 0.4443687schooling + 8.1986416incomeComp


#------------------------------------------
#R2:
##Answer: 61.94% of the variation is explained by the independent variable in the model



#------------------------------------------
#Hypothesis Testing:Schooling

#Answer p-value: 0.0000000000000002 < 0.05
#Decision/Response: Reject the null hypothesis [that schooling is not significant]; schooling is significant in predicting LifeExpectancy


#------------------------------------------
#------------------------------------------
#Hypothesis Testing:IncomeComp

#Answer p-value: 0.0000000000000002 < 0.05
#Decision/Response: Reject the null hypothesis [that schooling is not significant]; IncomeComp is significant in predicting LifeExpectancy


#------------------------------------------
```

## Complete the following: Prediction and Confidence Interval

-   Calculate the predicted LifeExpectancy with an AdultMortality rate of 280, SChooling average of 9, and IncomeComp of 0.50.
-   Construct a 95 percent confidence interval estimate for the mean LifeExpectancywith an AdultMortality rate of 280, SChooling average of 9, and IncomeComp of 0.50. (include correct interpretation)
```{r}
#------------------------------------------
#Predict Code 
66.1092771 - (0.0411909*280) + (0.4443687*9)+ (8.1986416*0.50)

#Answer/Statement: The LifeExpectancy with an AdultMortality rate of 280, SChooling average of 9, and IncomeComp of 0.50 = 62.67446 years

#------------------------------------------
#Confidence Interval Code
predict(LR3, data.frame(AdultMortality=280, Schooling=9,IncomeComp=0.50), interval="confidence")

#------------------------------------------
#Confidence Interval Interpretation Response/Statement: With 95% confidence, we can say the LifeExpectancy with 280 AdultMortality, Schooling of 9, and a IncomeComp of 0.50 would have a LifeExpectancy value between 62.37123 and 62.97769
#------------------------------------------
```


# Regression: Multiple Regression Problem 2

## Complete the following: Regression Model and Summary
-   Use a multiple regression model to predict the LifeExpectancy (Y) by using AdultMortality (X1), Schooling (X2), IncomeComp (X3) and GDP (X4). Call this model as LR4. 
**LifeExpectancy: Life Expectancy in age** | 
**AdultMortality: Adult Mortality Rates of both sexes (probability of dying between 15 and 60 years per 1000 population)** | 
**Schooling: Number of years of Schooling(years)** | 
**IncomeComp: Human Development Index in terms of income composition of resources (index ranging from 0 to 1)** |
**GDP: Gross Domestic Product per capita (in USD)**

-   Display the summary calculations for LR4.

```{r}
options(scipen=999)
#------------------------------------------
#Regression Model:
LR4 = lm(LifeExpectancy~AdultMortality+Schooling+IncomeComp+GDP, data=life)



#------------------------------------------
#Summary of Model:
summary(LR4)



#------------------------------------------
```

## Complete the following:  **Answer in chunk as a comment**: 

-   What is the estimated regression equation?
-   What percentage of the total variation in LifeExpectancy is explained by the regression (R2)?
-   Is GDP significant in predicting the LifeExpectancy at significance level of 0.05? To answer this question, we need to test Ho that H1= 0 against the two-sided alternative. Should the null hypothesis be accepted or rejected at a 0.05 significance level?
```{r}
#------------------------------------------
#Regression Equation:
#Answer: Y = 66.51736920 - 0.03988078AdultMortality + 0.40551758Schooling + 6.88723295Income + 0.00009348GDP


#------------------------------------------
#R2:
##Answer: 63.32% of the variation is explained by the independent variable in the model




#------------------------------------------
#Hypothesis Testing:GDP

#Answer p-value: 0.0000000000000002 p-value < 0.05
#Decision/Response: Reject the null hypothesis [that GDP is not significant]; GDP is significant in predicting house LifeEx[ectancy]


#------------------------------------------
```

## Complete the following: Prediction and Confidence Interval 

-   Calculate the predicted LifeExpectancy with an AdultMortality rate of 280, Schooling average of 9, IncomeComp of 0.50 and GDP of 430.
-   Construct a 95 percent confidence interval estimate for the mean LifeExpectancywith an AdultMortality rate of 280, SChooling average of 9, IncomeComp of 0.50, and GDP of 430. (include correct interpretation)
```{r}
#------------------------------------------
#Predict Code
66.51736920 - (0.03988078*280) + (0.40551758*9) + (6.88723295*0.50) + (0.00009348*430)


#Answer/Statement: The LifeExpectancy with an AdultMortality rate of 280, Schooling average of 9, IncomeComp of 0.50 and GDP of 430 is 62.48422

#------------------------------------------
#Confidence Interval Code
predict(LR4, data.frame(AdultMortality=280, Schooling=9,IncomeComp=0.50,GDP = 62.48422), interval="confidence")


#------------------------------------------
#Confidence Interval Interpretation Response/Statement: With 95% confidence, we can say the LifeExpectancy with 280 AdultMortality, Schooling of 9, a IncomeComp of 0.50, and a GDP of 62.48422 would have a LifeExpectancy value between 62.14923 and 62.7505
#------------------------------------------
```

# Knit to HTML



**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**