---
title: "Homework 6"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

# Cluster Analysis
Data taken from: https://www.kaggle.com/datasets/arjunbhasin2013/ccdata



## Question 1: Create a data frame loaded from creditcarddata.csv
```{r}
creditcard = read.csv("creditcarddata.csv")
```

## Question 2: Display the first 10 rows from the data frame called creditcard

```{r}
head(creditcard,10)
```

## Question 3: Create a new data frame creditcardNUM that will remove the non-numeric data from creditcard so we can procede with the K-Means analysis

```{r}
creditcardNUM = creditcard
creditcardNUM$CUST_ID = NULL
```


## Install factoextra and run the library

-   select the line below and click on Run selected line or Ctrl+Enter (Cmd+Enter)
-   having install.packages code within a chunk can cause issues when knitting to HTML

```{r}
library(factoextra)
```

## Visualize the Elbow Method and Silhouette Method, where the Elbow is that is the optimal number of K 
-   fviz_nbclust(creditcardNUM, kmeans, method = "wss")
-   fviz_nbclust(creditcardNUM, kmeans, method = "silhouette")

**Note this code may take a few moments to run**

```{r}
par(mfrow=c(1,2))
fviz_nbclust(creditcardNUM, kmeans, method = "wss")
fviz_nbclust(creditcardNUM, kmeans, method = "silhouette")
```


## Question 4: Set the seed and build a model for k=1 and k=2 using kmeans
-   Run K-Means for 1 cluster (k=1) and call the model km1
-   Run K-Means for 2 clusters (k=2) and call the model km2
-   Do not display the results, you will do that in the next few chunks
```{r}
set.seed(123)
#km1
km1 = kmeans(creditcardNUM,1)

#km2
km2 = kmeans(creditcardNUM,2)


```


## Question 5: Display the results for km1
```{r}
km1
```

## Question 6: Display the results for km2
```{r}
km2
```

## Question 7: Answer the following within the chunk as a comment: 
-   What are the cluster sizes for km2?
-   What is the average minimum payment for cluster2 compared to cluster1 for km2?
-   What is the average balance for cluster2 compared to cluster1 for km2?
-   What is the total sum of squares for km1?
-   What is the within sum of squares for 2 clusters (km2)? 
-   What is the total sum of squares for 2 clusters (km2)?
-   What is percent reduction from km1 to km2? 
```{r}
#---------------------------------------
#What are the cluster sizes for km2?
#Cluster 1: 1921 
#Cluster 2: 7029
#---------------------------------------
#What is the average minimum payment for cluster2 compared to cluster1 for km2?
#Cluster 1: 1753.9329 
#Cluster 2: 582.5646
1753.9329 - 582.5646
#Difference: 1171.368
#---------------------------------------
#What is the average balance for cluster2 compared to cluster1 for km2?
#Cluster 1: 3838.1596         
#Cluster 2: 943.0851         
3838.1596-943.0851
#Difference: 2895.074
#---------------------------------------
#What is the total sum of squares for km1?
#km1 total sum of squares: 393306778023
#---------------------------------------
#---------------------------------------
#What is the within sum of squares for 2 clusters (km2)? 
# 204726166357  74728388893
#---------------------------------------
#What is the total sum of squares for 2 clusters (km2)?
204726166357 +  74728388893
# 279454555250
#---------------------------------------
#What is percent reduction from km1 to km2? 
# 28.9% reduction 
#---------------------------------------
```


## Question 8: Add the cluster vector from km2 back to creditcard as column/variable cluster2
```{r}
creditcard$cluster2 = km2$cluster
```

## Question 9: Displays creditcard, ordered by cluster2 
-   dataframe[order(dataframe$column), ]

```{r}
creditcard[order(creditcard$cluster2), ]
```

## Question 10: Conceptually, take everything you have learned up to this point and look at the data to provide a brief thought on what you can do to further analyze this data now that there are 2 clusters. What can you do to compare or contrast the clusters? Just provide one to two examples (there are many possibilities). 
```{r}
#Commented Response: 
# The data in km2 is reduced from 100 percent down to 71.1% of the data, allowing for data that is more closely related to be analyzed. For example, analyzing payments that are closer to each other or balances that are closer to each other. The idea of clustering is to consolidate data that is close to each other. Hypothethicaly, as we increase the number of clusters the data in each cluster will be closer and closer, allowing outliers to not affect the data as much. 
```



Take the results for further analysis and profiling 

### Knit to HTML





**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**



