---
title: "Homework 8 Part 2"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

#   Optimization: Homework 8 Part 2

## Questions:

### Question 1: Formulate the linear programming model for this problem.
-   Use # to comment below each question (for each line)

```{r}
#----------------------------------
#a. Define the decision variables
#FoodItem1, FoodItem2,FoodItem3,FoodItem4


#----------------------------------
#b. Formulate the objective function
#minimize total cost = 1FoodItem1 + 0.4FoodItem2 + 0.6FoodItem3 + 1.8FoodItem4
 
#----------------------------------
#c. State the constraints.
# **LABEL THE CONSTRAINT | Do not forget to also list the non-negativity constraints**

# 400FoodItem1 + 200FoodItem2 + 150FoodItem3 + 500FoodItem4 >= 500 Calories 
#3FoodItem1 + 2FoodItem2 + 0FoodItem3 + 0FoodItem4 >= 6 grams of protein 
#2FoodItem1 + 2FoodItem2 + 4FoodItem3 + 4FoodItem4 >= 10 grams of carbohydrates
#2FoodItem1 + 4FoodItem2 + 1FoodItem3 + 5FoodItem4 >= 8 grams of protein 

#Non-Negativity 
#FoodItem1 >=0 
#FoodItem2 >=0 
#FoodItem3 >=0 
#FoodItem4 >=0 

#----------------------------------
``` 
 

### Install lpSolve and run the library

-   select the line below and click on Run selected line or Ctrl+Enter (Cmd+Enter)
-   having install.packages code within a chunk can cause issues when knitting to HTML


install.packages("lpSolve")



### Load the lpSolve library to use the lp function
-   Call the library function "lpSolve". You need to execute this library function each time when you run linear programming
```{r}
#no code needed this chunk, just run it
library (lpSolve) 
```




### Question 2:	Enter the problem data and find the optimum solution for this problem using R Studio 
-   Load the elements: 

-   objective, constr, constr.dir, rhs (from cheat sheet)  -OR-
-   ObjFunc, LeftSide, OpDirections, RightSide (from textbook/demo) 

```{r}
ObjFunc = c(1, 0.4, 0.6,1.8) #-   #minimize total cost = 1FoodItem1 + 0.4FoodItem2 + 0.6FoodItem3 + 1.8FoodItem4

leftsidevector = c(400,200,150,500,3,2,0,0,2,2,4,4,2,4,1,5)

LeftSide = matrix(leftsidevector, nrow = 4, byrow=TRUE)

OpDirections = c(">=",">=",">=",">=")
RightSide = c(500,6,10,8)

```

### Question 3: Run the lp function (optimum code from cheat sheet; lpmodel from textbook/demo)
```{r}
lpmodel = lp(direction = "min", ObjFunc, LeftSide, OpDirections, RightSide, compute.sens = T)
```


### Question 4: Display the solutions from the optimum solution 
-   a. Display the solution values 
-   b. Display the objective value 
-   c. Display the dual values 
```{r}
lpmodel$solution
lpmodel$objval
lpmodel$duals



```

### Question 5: Answer the questions inside the chunk using # to comment 
-   What are the dual values for the calorie, protein, carbohydrate, and fat requirements?
-  How much would the cost increase if the diet required one additional gram of calorie (501 grams instead of 500)? 
```{r}
#--------------------
# What are the dual values for the calorie, protein, carbohydrate, and fat requirements?
#Calorie = 0.00
#Protein = 0.05
#Carbohydrate = 0.15
#Fat = 0.00


#--------------------
# How much would the cost increase if the diet required one additional gram of calorie (501 grams instead of 500)? 

# It would increase by 0 



#--------------------
```




### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

