---
title: "Homework 8 Part 1"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---


**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

#   Optimization: Homework 8 Part 1

## Questions:

### Question 1: Formulate the linear programming model for this problem.
-   Use # to comment below each question (for each line)
```{r}
#----------------------------------
#a. Define the decision variables
#kettlebells, dumbells, plates



 
#----------------------------------
#b. Formulate the objective function
     
#maxmize profit = 50k + 25d + 40p

    
 
#----------------------------------
#c. State the constraints.
# **LABEL THE CONSTRAINT | Do not forget to also list the non-negativity constraints**
#2k + 0.5d+ 1p <= 250 labor hours 
#1k + 0.5d + 1p <= 200 machine hours 
#25k + 10d + 25p <= 4000 raw material
#0k + 1d + 0p <=200 steel

#k>=0
#d>=0
#p>=0

#----------------------------------
``` 
 

### Install lpSolve and run the library

-   select the line below and click on Run selected line or Ctrl+Enter (Cmd+Enter)
-   having install.packages code within a chunk can cause issues when knitting to HTML


install.packages("lpSolve")



### Load the lpSolve library to use the lp function
-   Call the library function "lpSolve". You need to execute this library function each time when you run linear programming
```{r}
#no code needed this chunk, just run it
library (lpSolve) 
```



### Question 2:	Enter the problem data and find the optimum solution for this problem using R Studio 
-   Load the elements: 

-   objective, constr, constr.dir, rhs (from cheat sheet)  -OR-
-   ObjFunc, LeftSide, OpDirections, RightSide (from textbook/demo) 

```{r}

ObjFunc = c(50, 25, 40) #-   #maxmize profit = 50k + 25d + 40p

leftsidevector = c(2,0.5,1,1,0.5,1,25,10,25,0,1,0)

LeftSide = matrix(leftsidevector, nrow = 4, byrow=TRUE)

OpDirections = c("<=","<=","<=","<=")
RightSide = c(250,200,4000,200)


```

### Question 3: Run the lp function (optimum code from cheat sheet; lpmodel from textbook/demo)
```{r}
lpmodel = lp(direction = "max", ObjFunc, LeftSide, OpDirections, RightSide, compute.sens = T)
```


### Question 4: Display the solutions from the optimum solution 
-   a. Display the solution values 
-   b. Display the objective value 
-   c. Display the dual values 
```{r}

lpmodel$objval
lpmodel$solution
lpmodel$duals


```

### Question 5: Answer the questions inside the chunk using # to comment 
-   What are the dual values? List and label each.
-   How much would the profit increase if we had 10 more pounds of steel on hand?
-   Should you purchase additional pounds of raw material if a supplier offered you 100 pounds of raw material for 1100? Briefly, why or why not? 
-   How much would the profit increase if we had one additional unit of labor (hour)?
```{r}
#--------------------
# What are the dual values? List and label each.

#labor 10.0
#machine 0.0
# raw 1.2
#steel 8.0  
#Kettlebells 0.0
#Dumbells 0.0  
#plates 0.0


#--------------------
# How much would the profit increase if we had 10 more pounds of steel on hand?

# 80 dollars 


#--------------------
# Should you purchase additional pounds of raw material if a supplier offered you 100 pounds of raw material for 1100? Briefly, why or why not? 

#No 1.2*100 equal 120 not 1200 or 1100, thus you lose 980 


#--------------------
#	How much would the profit increase if we had one additional unit of labor (hour)?

#10 dollars 


#--------------------
```




### Knit to HTML




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**

