---
title: "Midterm Exam"
author: "Ryan Hensley"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_download: yes
    toc: yes
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**


# Midterm Exam: 30 points Total 
-   Good Luck!
-   Make sure to review the Coding Policy posted to SAKAI to avoid losing points. Submit the Word Document to SAKAI alongside your Exam (no late work)!

**---------------------------------------------------------------------------------------**

# START: Data Types and Structures | Data Cleaning and Manipulaton 
-   8 Points

**---------------------------------------------------------------------------------------**


## Load: Read the data from occup5.csv creating a new data frame called occup5 
```{r}
#Code: nothing needed this chunk, just run it
occup5<-read.csv("occup5.csv")
```

## Look at the data: Display the first 6 rows of the data frame object occup5
```{r}
#Code: 
head(occup5)
```

## NAs: Take a look at the number of NA (blank values), complete the following:
-   a. How many NA values are in the hours column? Code and response. 
-   b. What is the average hours (hint: remember if there are NA values you need rm.na=TRUE see cheat sheet) Code and response. 
-   c. Change the NA values to the mean average hours   **only for the hours Column** 
-   d. Remove the column occupID from occup5 (the first column)
```{r}
#------------------------------------
#Code (a.): 
sum(is.na(occup5$hours))

#Response (a.): 2
#------------------------------------
#Code (b.): 
mean(occup5$hours,na.rm=TRUE)

#Response (b.): 47.21739
#------------------------------------
#Code (c.): 
occup5$hours[is.na(occup5$hours)] = 47.21739



#------------------------------------
#Code (d.): 
occup5$occupID = NULL

```

## Subset for non-NA: Create a subset (called occup5NoNA) that will remove all remaining rows with a NA value (na.omit) from occup5
-   How many rows were removed from occup5 to occup5NoNA? Response. 
```{r}
#------------------------------------
#Code: 
occup5NoNA = na.omit(occup5)
nrow(occup5)
nrow(occup5NoNA)

#Response: 1 

```


## Data Types: Review the data frame occup5NoNA Change the columns/variables to the most fit data type. **Make sure to use occup5NoNA this chunk**
-   a. The data should have the following (total 7 columns): 2 factor, 2 integers (educ and age), 3 numeric. 
-   b. Run str(occup5NoNA) 
```{r}
#------------------------------------
#Code (a.): 
str(occup5NoNA)
occup5NoNA$satisfaction = as.factor(occup5NoNA$satisfaction)
occup5NoNA$important = as.factor(occup5NoNA$important)



#------------------------------------
#Code (b.): 

str(occup5NoNA)

```


**---------------------------------------------------------------------------------------**

# END: Data Types and Structures | Data Cleaning and Manipulaton 

**---------------------------------------------------------------------------------------**

**---------------------------------------------------------------------------------------**

# START: Descriptive Analytics 
-   6 Points

**---------------------------------------------------------------------------------------**

## Load: Read the data from standardtests.csv creating a new data frame called results 
```{r}
#Code: nothing needed this chunk, just run it
results = read.csv("standardtests.csv")
```

## Display the summary stats for results and complete the following: 
-   a. Which column has the highest average between A, B, C, D, and E? 
-   b. What was the median number of passed exams?  
```{r}
#------------------------------------
#Code: 
summary(results)


#------------------------------------
#Response (a.): A

#Response (b.): 69.0

```

## Display a histogram for the variable passed; main="Passed Distribution", col = "orange"
-   a. Based on the result, provide the approximate range (x-axis) of the bin from the histogram with the highest frequency.
```{r}
#------------------------------------
#Code:
hist(results$Passed,main = "Passed Distribution", col = "orange")


#------------------------------------
#Response (a.): 100
```


## Display the frequency table for city and complete  the following:
-   a. How many tests were taken from Carbondale?
```{r}
#------------------------------------
#Code: 
table(results$City)


#------------------------------------
#Response (a.):32

```


## Display/tabulate the average Passed by the City for results.
-   a. What is the average Passed for Chicago? Response. 
```{r}
#------------------------------------
#Code: 
tapply(results$Passed,results$City,mean)

#------------------------------------
#Response (a.):130.5882

```



**---------------------------------------------------------------------------------------**

# END: Descriptive Analytics

**---------------------------------------------------------------------------------------**

**---------------------------------------------------------------------------------------**

# START: Predictive Analytics | Regression
-   14 Points

**---------------------------------------------------------------------------------------**

## Load: Read the data from insurance.csv creating a new data frame called insurance 
```{r}
#Code: nothing needed this chunk, just run it
insurance=read.csv("insurance.csv")
```


## Calculate the following correlation coefficients looking to build a model to predict the charges 
-   insurance (7 columns) looking to predict charges
-   a. Which variable has the highest absolute correlation to charges?
```{r}
#------------------------------------
#Code: 
cor(insurance$charges,insurance[,1:7])

#------------------------------------
#Response (a.): smoker

```

## Complete the following: Regression Model and Summary
-   Use a simple regression model to predict charges by using the highest correlated variable from the previous chunk as the independent variable. Call this model as R1
-   Display the summary calculations for R1
```{r}
options(scipen=999)
#------------------------------------------
#Regression Model:
R1 = lm(charges~smoker,data = insurance)

#------------------------------------------
#Summary of Model:
summary(R1)


#------------------------------------------
```


## Complete the following:  **Answer in chunk as a comment**: 

-   What is the estimated regression equation?
-   What percentage of the total variation in charges is explained by the regression (R2)?
-   Is the independent variable significant in predicting the charges at significance level of 0.05? To answer this question, we need to test Ho that H1= 0 against the two-sided alternative. Should the null hypothesis be accepted or rejected at a 0.05 significance level?
-   Conceptual Question: Keep it simple, what is the difference of a positive and negative correlation? 

```{r}
#------------------------------------------
#Regression Equation:
#Answer: Y = 8543.4 + 23536.5x


#------------------------------------------
#R2:
##Answer: 0.6188 or 61.88% of the variation is is explained by the independent variable in the model



#------------------------------------------
#Hypothesis Testing:

#Answer p-value: 0.0000000000000002 < 0.05
#Decision/Response: Reject the null hypothesis [that smoker is not significant]; smoker is significant in predicting charges


#------------------------------------------
# Conceptual Question Response: Postive correlation means that as one value goes up the other also goes up. Negative correltaion is as one goes up the other goes down.

#------------------------------------------
```


## Complete the following: Prediction and Confidence Interval

-   Calculate the predicted average charges using a value of 1 for the independent variable.
-   Construct a 95 percent confidence interval estimate for the mean charges using 1 for the independent variable value. (include correct interpretation)
```{r}
#------------------------------------------
#Predict Code
8543.4 + (23536.5*1)

#Answer/Statement: the predicted average charges for a indiviudal with an smoker rate of 1 Is 32079.9 dollars

#------------------------------------------
#Confidence Interval Code

predict(R1, data.frame(smoker=1), interval="confidence")

#------------------------------------------
#Confidence Interval Interpretation Response/Statement: With 95% confidence, we can say the charges with an smoker value of 1 would have a charges between 31143.69 and 33015.99
#------------------------------------------
```

**---------------------------------------------------------------------------------------**

# END: Predictive Analytics | Regression

**---------------------------------------------------------------------------------------**



# Knit to HTML
-   2 points overall knit and completion
-   Make sure to review the Coding Policy posted to SAKAI to avoid losing points. Submit the Word Document to SAKAI alongside your Exam (no late work)!




**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites for all content provided.**