---
title: "Business Analytics Midterm EC"
subtitle: Business Analytics
author: "Your Name Here"
output:
  html_document: 
   code_download: yes
   toc: yes
---

**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites.**

**Be sure to read all the instructions and answer each question in-full. Submit the output in RMD and HTML.**

**YOU DO NOT NEED TO CREATE ANY CHUNKS. RESPOND USING THE CHUNKS AND PROMPTS PROVIDED.**

**DO NOT MODIFY ANY OF THE FORMATTING OF THE RMD.**


Submit your R Markdown (RMD) and HTML to SAKAI

**All interpretations are essential for points.**
-   Meaning if the response requires a conceptual interpretation, do not just respond with the value R provide
-   For instance, confidence intervals require proper interpretation (STATS REF)

------------------------------------------------------------------------
# Begin: Cleaning and Manipulation
-   Data Types and Structures | NA Values
------------------------------------------------------------------------

**For this portion you will use the SchoolPreference.csv file**

## Read the file SchoolPreference.csv into R as a dataframe
-   Call the data frame object school
```{r read_file}
#Code: next line- nothing needed this chunk, you will use school for the descriptive section
school<-read.csv("SchoolPreference.csv")
```


## Display the first 10 rows of the dataframe loaded (school)
```{r display_results}
#Code: next line 


```

## Display the structure of the columns of the data frame loaded (school)
-   Look at each of the variables/columns loaded and notice which data types need modification which you will change in the next few chunks
```{r structure_school}
#Code: next line 



```

## Complete the following for the PerctBlended column:
-   a. How many NA values are in the PerctBlended column? 
-   b. Change the NA values to 0 -- only for the PerctBlended Column**
```{r na_PerctBlended}
#Code: Number of NA values in PerctBlended 


#Answer the question as a comment:
  ##Number of NA values in PerctBlended: 


#Code: Change NA values to 0 only in PerctBlended


```


## Looking at the data types, change the data to the appropriate data types
-   a. There should be 3 factors
-   b. There should be 3 integers
-   c. There should be 2 numeric (num)
-   d. Change the necessary columns to the appropriate data type (you may only need to change 3 depending on how the data loaded)
```{r datatypes_school}
#Code: next line to change any column/variable data types 




#Run str(school) to check results



```

## Create a subset that you will use later on, call this subset schoolAll
-   To create the subset, use the column Category and only include those rows that have a value equal to All District
```{r subset_AllDistrict}
#Code: next line subset Category


```

## Create a vector, call it fullname and assign your first name and last name as two separate values (so one vector with 2 values assigned). After, display the vector fullname

**Not using school, just creating a vector and displaying the vector**
```{r vector_fullname}
#Code: next line create vector fullname


#Code: next line display vector fullname


```

----------------------------------------------------------------------
# End:  Data Cleaning and Manipulation 
----------------------------------------------------------------------

----------------------------------------------------------------------
# Begin: Descriptive Analytics
- Summary Statistics | Visualizations
----------------------------------------------------------------------

**For this portion you will use the school subset schoolAll created in the Data Cleaning and Manipulation section above**

**You will need to complete the Data Cleaning and Manipulation section prior to starting the Descriptive Analytics below**


## Display summary statistics for ALL variables in the schoolAll data frame and answer the question.
-   use the summary output to answer the questions within the chunk (commented)
-   Question: What is the average Total Enrollment, PerctBlended, PerctRemote for the data schoolAll? Which Learning is preferred?
```{r display_sumresults}
#Code: next line using schoolAll


#Answer the following as a comment:
  ##Average Total Enrollment:         
  ##Average PerctBlended:             
  ##Average PerctRemote:              
  ##Based on the results of PerctBlended and PerctRemote, what is the preference-- Blended Learning or Remote Learning?: 

```



**USE schoolAll**


## Run the code that will display the average/mean NumRemote by District using schoolAll
-   Which District had the largest average for NumRemote? Answer after the chunk.

**Hint: the output of the table format should look like**
-   **1       2     3        etc.**
-   **[#]     [#]   [#]      etc.**
```{r mean_NumRemotebyDistrict}
#Code: next line using schoolAll


#Answer the following as a comment:
  ##District Number with Highest NumRemote: 

```


------------------------------------------------------------------------
# End:  Descriptive Analytics
------------------------------------------------------------------------




------------------------------------------------------------------------
# Begin: Predictive Analytics
- Regression 
------------------------------------------------------------------------
## Regression: For this portion you will use the TSLA.csv file

## Read the file TSLA.csv into R as a data frame.
-   Call the data frame object tesla
```{r read_file_tesla}
#Code: next line
tesla<-read.csv("TSLA.csv")
```


## Displaying Tesla-no code needed in this chunk, make sure the data types loaded in correctly (do not worry about converting the date)
-   Date, Open, High, Low, Close, Volume refer to Tesla stock data
```{r display_tesla}
head(tesla)
str(tesla)
```


## Calculate the following correlation coefficients looking to build a model to predict the Close (price) of the tesla stock
-   tesla (4 columns) looking to predict Close
## Answer the following:
-   Which relationship has the highest correlation with Close?
-   Which relationship has the second highest correlation with Close?

```{r cor_tesla}
#Code: next line for cor() -- you will need 4 cor() statements



#Answer the following as a comment:
  ##Highest correlation co-efficient (comment the column name): 
  ##Second highest correlation co-efficient (comment the column name): 

```




# Simple Regression:

## Use a simple regression model to predict the Close price from tesla by using the highest correlated variable from the previous chunk
-   Call this model as R1. Display the summary calculations in R1.
```{r regression_m}
options(scipen=999)
#Code: Regression Model R1


#Code: Summary calculations R1


```

## Using the summary results from the previous chunk, comment the following answers: 
-   a. What is the estimated regression equation?
-   b. What percentage of the total variation in charges is explained by the regression (R_square)? -   c. Hypothesis: Is the number of [Highest Correlated Variable] significant in predicting the charges at significance level of 0.05?

```{r}
#Answer the following as a comment (no code this chunk):
  #Answer (a. Regression Equation): Y = 
  #Answer (b. R-Squared): 
  #Answer (c. Hypothesis Testing): answer the p-value and Decision
    #p-value (< or > alpha of 0.05): 
    #Decision: 

```

## Calculate the predicted charges of the Independent variable Use the value 95 
```{r}
##Code Next line to predict where your independent variable is equal to 95:


```

## Construct a 95 percent confidence interval estimate of the Independent variable Use the value 95 
```{r predictreg}
#Code: Predict: Confidence Interval


#Answer the following as a comment:
  ##Answer (Response): 

```

**Note for Fall23: Expect a few conceptual questions from slides and text built in as well.**


------------------------------------------------------------------------
# End:  Predictive Analytics
------------------------------------------------------------------------
------------------------------------------------------------------------
# End:  
------------------------------------------------------------------------


### CREATE HTML FILE
Create an html file that will contain 
    #	all the codes 
    #	executed outputs and 
    #	answers to the follow-up questions, if there is any. 
    
    
    
**Copyright Kaitlyn Hoffmann, All rights reserved. Not for resale, distribution, or posting to external sites.**